QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-10-10 Response/Paper_Res.tex
Rev_V5.7

\begin{my}{1cm}{1cm}
	\rev{  }
\end{my}

@@

@@

\end{itemize}}}
\end{my}
\vspace{5mm}

@@

	\underline{Authors' Reply}: To address the reviewer's comment, we have included Table. 1 in the 'Related Works' Section II  subsection that highlights the key characteristics of relevant studies.
	\begin{table*}[htbp]\textcolor{blue}{
			\renewcommand{\arraystretch}{0.6}
			\captionsetup{name=TABLE}
			\caption{\textcolor{blue}{Comparison of Related Works \vspace{4mm}}}
			\scalebox{0.7}{%
				\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3.1cm}p{4.6cm}l} 
					\toprule
				\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDPG + DDQN & Only for a singel MEC system model  \\\midrule
\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule				
\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
\cite{wu2023computation} & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
\cite{wu2024combining} & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
\cite{wu2023multi} & Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent DQN&  Not consider tasks with maximum delay tolerance \\\midrule
\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
\cite{Bolourian-WCL24} & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
					\toprule
			\end{tabular}}
			\label{table1}}
	\end{table*}

\newpage
	\item \underline{Reviewer's Comment}: 
	\textit{``I think more explanations should be added for the QoE function. How can the defined function reflect QoE?''} \newline

@@

The QoE function evaluates the influence of agent's actions based on its personalized QoE requirement, by taking several key performance factors into account. It incorporates a multi-dimensional and adaptive structure that establishes an appropriate balance among these QoE factors according to the MD's preference, such as individual preferences for reducing task delays or energy consumption, which may vary over time. To reflect the agent’s personalized QoE requirements, an adaptive trade-off between task completion and cost reduction is designed, where a weighted sum between completion delay and energy consumption plays as an associated cost. The MDs adjusted the weights dynamically to define the significance of each factor based on its energy mode—performance, power-saving, or ultra power-saving. 
		Based on the system model, we first formulate the calculation of task delay and energy consumption and then represent the associated cost and QoE function accordingly. \vspace{3mm}

	Given the selected action $\boldsymbol{a}_i(t)$ in the observed state $\boldsymbol{s}_i(t)$, we represent $\mathcal{D}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t))$ as the delay of task $z_i(t),$ which indicates the number of time slots from time slot $t$ to the time slot in which task $z_i(t)$ is processed. It is calculated by: \vspace{2mm}

	$\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t))\Big(l_i^{\text{C}}(t) - t + 1\Big)  +  x_i(t)$
	\begin{alignat}{1}
		\hspace{50mm}\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t'=t}^{T} \mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big) \textcolor{blue}{y_{i,j}(t)} \, l_{i,j}^{\text{E}}(t') - t +1\bigg),
		\label{21}  
	\end{alignat} 
where $\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))= 0$ if task $z_i(t)$ is dropped. Accordingly, the energy consumption for task $z_i(t)$ under action $\boldsymbol{a}_i(t)$ in observed state $\boldsymbol{s}_i(t)$ is denoted as $\mathcal{E}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t))$, given by:
	\begin{alignat}{1}
\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t)) E_i^{\text{L}}(t)+  x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t^{'}=t}^{T}\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big) \textcolor{blue}{y_{i,j}(t)}  E_i^{\text{O}}(t)  \bigg).
		\label{22}  
	\end{alignat}
To define associated cost, we use a weighted sum between task delay $\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ and energy consumption $\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$, where the weights adjust dynamically depending on the MD's energy levels to reflect the MD's preference for each factor.
		Given the delay and energy consumtion of task $z_i(t)$, we define $\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ that denotes the assosiate cost of task $z_i(t)$ given the action $\boldsymbol{a}_i(t)$ in the state $\boldsymbol{s}_i(t)$.
	\begin{alignat}{1}
		\,\,\,\,\,\,\,\, \mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = \phi_i(t) \, \mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) +(1-\phi_i(t)) \, \mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)),
		\label{23}  
	\end{alignat}
	where $\phi_i(t)$ represents the MD $i$'s \textcolor{blue}{energy level}. 
When the MD is operating in performance mode, the MD's preference is to minimize task delays, thus the delay contributes more to the cost than energy consumption. In contrast, when it switches to ultra power-saving mode, the main attention is directed toward reducing energy consumption and the energy consumption contributes more to the cost than delay.
	Finally, we define an adaptive trade-off between task completion and cost reduction as the QoE associated with task $z_i(t)$. The QoE is affected by the increase in the number of completed tasks given by the task's complexity and reducing weighted cost. Given the selected action $\boldsymbol{a}_i(t)$ and the observed state $\boldsymbol{s}_i(t)$, we define The QoE function as follows,
		\begin{alignat}{1}
			\boldsymbol{q}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = 	\mathcal{R}\, \lambda_i(t) \rho_i(t) - \mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))
	\end{alignat}
	where $\mathcal{R} > 0$ represents a constant reward for task completion. If $z_i(t) = 0$, then $\boldsymbol{q}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t)) = 0$. Throughout the rest of this paper, we adopt the shortened notation $\boldsymbol{q}_i(t)$ to represent $\boldsymbol{q}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t))$.

@@

>>>>

\begin{my}{1cm}{1cm}
	\rev{

\textcolor{blue}{\,\,\,\,To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} hold promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives.
	While RL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. 
	QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.} \vspace{2mm}

\textcolor{blue}{\,\,\,\,In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging deep DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.}

 }
\end{my}

@@

			\textcolor{blue}{\,\,\,\,In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging deep DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.} \vspace{2mm}

@@

\dots
}}
\end{my}
\vspace{5mm}

@@

	\underline{Authors' Reply}: To address the reviewer's comment, we have carefully studied the recently published papers and revised the manuscript. 
	To be more specific,
	\begin{itemize}
		\item a)
		We have extended the literature review in Section II of the revised manuscript by providing a more comprehensive survey of the recently published state-of-the-art works and comparing their methods characteristics in Table I.

		\item b)  We have compared our work with more existing works and extended the performance evaluation in Section V of the revised manuscript.

\vspace{6mm}
	a) The newly added Section II of the revised manuscript is as follows.

\begin{my}{1cm}{1cm}
	\rev{
		\section{Related Work}
		\label{section:II}
		\,\,\,\,In recent years, edge computing has become a popular method for scenarios that need to process massive data with weak devices, such as IoTs \cite{zhang2023multi}, Internet of Vehicles (IoVs) \cite{lin2022multi}, \cite{wei2023many}, and Industrial IoT (IIoT) \cite{yuan2023adaptive} environment.
		We explore state-of-the-art RL-based techniques characteristic to discuss how they address task offloading problems in MEC. Table I provides an intuitive comparison of the related works.
		\subsection{DRL-based Computation Offloading for MEC}
		\,\,\,\,To effectively tackle the challenges of MEC arising from the ever-changing nature of networks, recent research highlights the effectiveness of RL in adapting to environmental changes and learning optimal strategies. To take advantage of RL methods for computation offloading in MEC, most studies transfer the problem to MDP to model the interactions of the environment.
		Huang \textit{et al.} in \cite{huang2019deep}, focused on a wireless-powered MEC and proposed a DRL-based approach, capable of attaining near-optimal decisions. This is achieved by selectively considering a compact subset of candidate actions in each iteration. Liu \textit{et al.} in \cite{liu2021learn} investigated a two-timescale computing offloading and resource allocation problem and proposed a resource coordination algorithm based on multi-agent DRL, which can generate interactive information along with resource decisions. 
		Wu \textit{et al.} in \cite{wu2023computation} introduced a stochastic game-based resource allocation in the SDN-based MEC network. They used an MDP and proposed a multi-agent RL method to minimize both energy consumption and processing delay. Zhou \textit{et al.} in \cite{zhou2021deep} proposed a Q-learning approach, which is an extension of RL to achieve optimal resource allocation strategies and computation offloading. 
		These works in \cite{huang2019deep}, \cite{liu2021learn} do not account for delay-sensitive tasks and may overlook critical performance factors in real-time applications. Besides, these studies \cite{huang2019deep}--\cite{zhou2021deep} primarily investigate simplified MEC networks, focusing on single MEC network models, considering only single-server or single-user scenarios, which may not always reflect real-world scenarios. 
		Moreover, due to the absence of robust underlying resource scheduling systems, issues such as data congestion during transmission and resource allocation can arise, leading to suboptimal system performance. Therefore, more accurate MEC models are needed to address the complexities of dynamic resource scheduling in large-scale scenarios. \vspace{2mm}

We have also revised Section I accordingly to highlight the contribution further and make it consistent with the updated contents of related work. The following paragraph shows the changes we have made in Section I of the revised manuscript.

\begin{my}{1cm}{1cm}
	\rev{

		\textcolor{blue}{\,\,\,\,To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} hold promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives.
			While RL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. 
			QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.} \vspace{2mm}

		\textcolor{blue}{\,\,\,\,In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging deep DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.} \vspace{2mm}
		Our main contributions are summarized as follows:
		\begin{itemize}
			\item \textit{Task Offloading Problem in the MEC System:} We formulate the task offloading problem in queuing-based MEC as an MDP for time-sensitive tasks, taking into account the time-varying system environments (e.g., the arrival of new tasks, and the computational requirement of each task). Given task completion, task delay, and energy consumption as the QoE requirements of mobile devices (MDs), this approach concentrates on maximizing the long-term QoE, by effectively utilizing the resources and properly handling the dynamic nature of workload at ENs. \vspace{2mm}

	}

\end{my} \vspace{6mm}

b) We extended the evaluation of the QECO algorithm by comparing it with DCDRL \cite{qiu2020distributed}, which is a distributed optimization algorithm for delay-sensitive tasks based on the actor-critic framework. This is the foundation for many state-of-the-art DRL algorithms, including DDPG and PPO. We have added this comparison to Section V of the revised manuscript as follows: 
\begin{my}{1cm}{1cm}
	\rev{
		{\

	We use the following methods as benchmarks.
			\begin{itemize}

	\item \underline{Reviewer's Comment}: 
	\textit{``I think more explanations should be added for the QoE function. How can the defined function reflect QoE?''} \newline

@@

The QoE function evaluates the influence of agent's actions based on its personalized QoE requirement \cite{wang2017qoe}, by taking several key performance factors into account. It incorporates a multi-dimensional and adaptive structure that establishes an appropriate balance among these QoE factors according to the MD's preference, such as individual preferences for reducing task delays or energy consumption, which may vary over time \cite{wang2019intelligent}, \cite{mehrabi2019energy}. To reflect the agent’s personalized QoE requirements, an adaptive trade-off between task completion and cost reduction is designed, where a weighted sum between completion delay and energy consumption plays as an associated cost. The MDs adjusted the weights dynamically to define the significance of each factor based on its energy mode—performance, power-saving, or ultra-power-saving. 
Based on the system model, we first calculate task delay and energy consumption and then represent the associated cost and QoE function accordingly.

				To define associated cost, we use a weighted sum between task delay $\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ and energy consumption $\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$, where the weights adjust dynamically depending on the MD's energy levels to reflect the MD's preference for each factor. \\\dots
}}
	\end{my}\vspace{6mm}

We have also revised the explanation related to Fig. 6 and Fig. 7 in Section V of the revised manuscript to further specify how the QECO algorithm improves QoE for users. The following paragraph shows the changes we have made in Section V of the revised manuscript.
\begin{my}{1cm}{1cm}
	\rev{
		{\

\end{my}\vspace{6mm}

@@

	\begin{my}{1cm}{1cm}
		\rev{

			We consider a MEC environment with 50 MDs and 5 ENs, similar to \cite{9253665}. We also follow the model presented in \cite{zhou2021deep} to determine the energy consumption. All the parameters are given in Table~\ref{table}. To train the MDs' neural networks, we adopt a scenario comprising 1000 episodes. Each episode contains 100 time slots, each of length 0.1 second. The QECO algorithm incorporates real-time experience into its training process to continuously enhance the offloading strategy. Specifically, we employ a batch size of 16, maintain a fixed learning rate of 0.001, and set the discount factor $\gamma$ to 0.9. The probability of random exploration gradually decreases from an initial value 1, progressively approaching 0.01, all of which is facilitated by an RMSProp optimizer. The algorithm's source code is available at \cite{QECO}.

			\dots
	}
	\end{my} \vspace{6mm}

### 2024-10-10 Revision/Paper_Rev.tex
Rev_V5.7

\subsection{QoE Function}
%\textcolor{brown}{The QoE function evaluates the influence of agent's actions based on its personalized QoE requirement, by taking several key performance factors into account. It incorporates a multi-dimensional and adaptive structure that establishes an appropriate balance among these QoE factors according to the MD's preference, such as individual preferences for reducing task delays or energy consumption, which may vary over time. To reflect the agent’s personalized QoE requirements, an adaptive trade-off between task completion and cost reduction is designed, where a weighted sum between completion delay and energy consumption plays as an associated cost. The MDs adjusted the weights dynamically to define the significance of each factor based on its energy mode—performance, power-saving, or ultra power-saving. When the MD is operating in performance mode, the MD's preference is to minimize task delays. In contrast, when it switches to ultra power-saving mode, the main attention is directed toward reducing energy consumption. Based on the system model, we first formulate the calculation of task delay, energy consumption, and associated cost, and then represent the QoE function accordingly.}

\textcolor{blue}{The QoE function evaluates the influence of agent's actions based on its personalized QoE requirement, by taking several key performance factors into account. It incorporates a multi-dimensional and adaptive structure that establishes an appropriate balance among these QoE factors according to the MD's preference, such as individual preferences for reducing task delays or energy consumption, which may vary over time. To reflect the agent’s personalized QoE requirements, an adaptive trade-off between task completion and cost reduction is designed, where a weighted sum between completion delay and energy consumption plays as an associated cost. The MDs adjusted the weights dynamically to define the significance of each factor based on its energy mode—performance, power-saving, or ultra power-saving. 
Based on the system model, we first formulate the calculation of task delay and energy consumption and then represent the associated cost and QoE function accordingly.}

@@

$\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t))\Big(l_i^{\text{C}}(t) - t + 1\Big)  +  x_i(t)$
\begin{alignat}{1}
	\;\;\;\,\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t'=t}^{T} \mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big) \textcolor{blue}{y_{i,j}(t)} \, l_{i,j}^{\text{E}}(t') - t +1\bigg),
	\label{21}  
\end{alignat} 
\textcolor{blue}{where $\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))= 0$ if task $z_i(t)$ is dropped. Accordingly, the energy consumption for task $z_i(t)$ under action $\boldsymbol{a}_i(t)$ in observed state $\boldsymbol{s}_i(t)$ is denoted as $\mathcal{E}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t))$, given by:}\vspace{2mm}

@@

\textcolor{blue}{To define associated cost, we use a weighted sum between task delay $\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ and energy consumption $\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$, where the weights adjust dynamically depending on the MD's energy levels to reflect the MD's preference for each factor.
Given the delay and energy consumtion of task $z_i(t)$, we define $\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ that denotes the assosiate cost of task $z_i(t)$ given the action $\boldsymbol{a}_i(t)$ in the state $\boldsymbol{s}_i(t)$.} \vspace{2mm}

$\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) =$
\begin{alignat}{1}
\,\,\,\,\,\,\,\,\phi_i(t) \, \mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) +(1-\phi_i(t)) \, \mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)),
	\label{23}  
\end{alignat}
where $\phi_i(t)$ represents the MD $i$'s \textcolor{blue}{energy level}. 
\textcolor{blue}{When the MD is operating in performance mode, the MD's preference is to minimize task delays, thus the delay contributes more to the cost than energy consumption. In contrast, when it switches to ultra power-saving mode, the main attention is directed toward reducing energy consumption and the energy consumption contributes more to the cost than delay.}

\textcolor{blue}{Finally, we define an adaptive trade-off between task completion and cost reduction as the QoE associated with task $z_i(t)$. The QoE is affected by the increase in the number of completed tasks given by the task's complexity and reducing weighted cost. Given the selected action $\boldsymbol{a}_i(t)$ and the observed state $\boldsymbol{s}_i(t)$, we define The QoE function as follows,
\begin{alignat}{1}
\boldsymbol{q}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = 	\mathcal{R}\, \lambda_i(t) \rho_i(t) - \mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))
\end{alignat}}
%\begin{alignat}{1}
% \hspace*{1mm}
%	\begin{cases} 
%		\mathcal{R}( \lambda_i(t) \rho_i(t)) - \mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) & \hspace*{-2mm} \text{if task $z_i(t)$ is processed,} \\
%		- \hspace*{0.8mm} \mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) &	\hspace*{-2mm} \text{if task $z_i(t)$ is dropped,}
%	\end{cases}
%	\label{26}  
%\end{alignat}
where $\mathcal{R} > 0$ represents a constant reward for task completion. If $z_i(t) = 0$, then $\boldsymbol{q}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t)) = 0$. Throughout the rest of this paper, we adopt the shortened notation $\boldsymbol{q}_i(t)$ to represent $\boldsymbol{q}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t))$.
%When $\phi_i(t)$ is closer to 1, the cost function prioritizes reducing delay and drop, which could be advantageous in situations where tasks need to be completed quickly, and responsiveness is crucial. Conversely, when $\phi_i(t)$ is closer to 0, the cost function prioritizes reducing energy consumption, which is beneficial when the MD's battery level is low, and conserving power is necessary to prolong operation.

@@

\subsection{Simulation Setup}
We consider a MEC environment with 50 MDs and 5 ENs, similar to \cite{9253665}. We also follow the model presented in \cite{zhou2021deep} to determine the energy consumption. All the parameters are given in Table~\ref{table}. To train the MDs' neural networks, we adopt a scenario comprising 1000 episodes. Each episode contains 100 time slots, each of length 0.1 second. The QECO algorithm incorporates real-time experience into its training process to continuously enhance the offloading strategy. Specifically, we employ a batch size of 16, maintain a fixed learning rate of 0.001, and set the discount factor $\gamma$ to 0.9. The probability of random exploration gradually decreases from an initial value 1, progressively approaching 0.01, all of which is facilitated by an RMSProp optimizer. \textcolor{blue}{The algorithm source code is publicly available in \cite{QECO}}.

>>>>

\subsection{QoE Function}
\textcolor{blue}{The QoE function evaluates the influence of agent's actions based on its personalized QoE requirement, by taking several key performance factors into account. It incorporates a multi-dimensional and adaptive structure that establishes an appropriate balance among these QoE factors according to the MD's preference, such as individual preferences for reducing task delays or energy consumption, which may vary over time. To reflect the agent’s personalized QoE requirements, an adaptive trade-off between task completion and cost reduction is designed, where a weighted sum between completion delay and energy consumption plays as an associated cost. The MDs adjusted the weights dynamically to define the significance of each factor based on its energy mode—performance, power-saving, or ultra power-saving. 
	Based on the system model, we first formulate the calculation of task delay and energy consumption and then represent the associated cost and QoE function accordingly.}

@@

$\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t))\Big(l_i^{\text{C}}(t) - t + 1\Big)  +  x_i(t)$
\begin{alignat}{1}
	\;\;\;\,\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t'=t}^{T} \mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big) \textcolor{blue}{y_{i,j}(t)} \, l_{i,j}^{\text{E}}(t') - t +1\bigg),
	\label{21}  
\end{alignat} 
where $\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))= 0$ if task $z_i(t)$ is dropped. Correspondingly, we denote the energy consumption of task $z_i(t)$ when taking action $\boldsymbol{a}_i(t)$ in the observed state $\boldsymbol{s}_i(t)$ as $\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$, which is: \vspace{1.7mm}

@@

\textcolor{blue}{To define associated cost, we use a weighted sum between task delay $\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ and energy consumption $\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$, where the weights adjust dynamically depending on the MD's energy levels to reflect the MD's preference for each factor.}
Given the delay and energy consumtion of task $z_i(t)$, we also define $\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ that denotes the assosiate cost of task $z_i(t)$ given the action $\boldsymbol{a}_i(t)$ in the state $\boldsymbol{s}_i(t)$. \vspace{1.7mm}

$\mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) =$
\begin{alignat}{1}
	\phi_i(t) \, \mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) +(1-\phi_i(t)) \, \mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)),
	\label{23}  
\end{alignat}
where $\phi_i(t)$ represents the MD $i$'s \textcolor{blue}{energy level}. When the MD is operating in performance mode, the primary focus is on minimizing task delays, thus the delay contributes more to the cost. On the other hand, when the MD switches to ultra power-saving mode, the main attention is directed toward reducing power consumption.

Finally, we define $\boldsymbol{q}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t))$ as the QoE associated with task $z_i(t)$ given the selected action $\boldsymbol{a}_i(t)$ and the observed state $\boldsymbol{s}_i(t)$. The QoE function is defined as follows:\vspace{1.7mm}

$\boldsymbol{q}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) =$
\begin{alignat}{1}
	\hspace*{8mm}
	\begin{cases} 
		\mathcal{R} - \mathcal{C}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) & \hspace*{-2mm} \text{if task $z_i(t)$ is processed,} \\
		- \hspace*{0.8mm} \mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) &	\hspace*{-2mm} \text{if task $z_i(t)$ is dropped,}
	\end{cases}
	\label{26}  
\end{alignat}
where $\mathcal{R} > 0$ represents a constant reward for task completion. If $z_i(t) = 0$, then $\boldsymbol{q}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t)) = 0$. Throughout the rest of this paper, we adopt the shortened notation $\boldsymbol{q}_i(t)$ to represent $\boldsymbol{q}_i(\boldsymbol{s}_i(t), \boldsymbol{a}_i(t))$.

@@

\subsection{Simulation Setup}
We consider a MEC environment with 50 MDs and 5 ENs, similar to \cite{9253665}. We also follow the model presented in \cite{zhou2021deep} to determine the energy consumption. All the parameters are given in Table~\ref{table}. To train the MDs' neural networks, we adopt a scenario comprising 1000 episodes. Each episode contains 100 time slots, each of length 0.1 second. The QECO algorithm incorporates real-time experience into its training process to continuously enhance the offloading strategy. Specifically, we employ a batch size of 16, maintain a fixed learning rate of 0.001, and set the discount factor $\gamma$ to 0.9. The probability of random exploration gradually decreases from an initial value 1, progressively approaching 0.01, all of which is facilitated by an RMSProp optimizer. \textcolor{blue}{The algorithm's source code is available at \cite{QECO}}.
